---
title: "Outbreak - Flexdashboard test"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r}
# Load packages
library(here)
library(tidyverse)
library (DT)
library(incidence2)
```

```{r}
# Import data
linelist <- read_rds(here("linelist_cleaned.rds"))
```

# Outbreak dashboard {.sidebar}
This dashboard aims to show possibilities of flexdashboard. 

Source:

https://epirhandbook.com/en/dashboards-with-r-markdown.html

This is a sidebar. It holds text viewable from any page.

# Overview
## Column 1 {data-width=500}
### Formulas in text and bullet points

This report is for the Incident Command team of the fictional outbreak of Ebola cases. **As of `r format(max(linelist$date_hospitalisation, na.rm=T), "%d %B")` there have been `r nrow(linelist)` cases reported as hospitalized.**  

* Several previously-unaffected areas to the West are now reporting cases  
* Internal reviews suggest that better communication is needed between district and provincial level data management teams  
* Safe and dignified burial teams are reporting difficulties  


### Table
The output will look best and respond to the window size if you use the kable() function from knitr to display your tables. The flextable functions may produce tables that are shortened / cut-off.
Info on kable: 
https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html

#### Cases by hospital
```{r}
linelist %>%
  count(hospital) %>%
  rename("Hospital" = hospital,
         "Cases" = n) %>% 
  knitr::kable()
```

## Column 2 {data-width=500}
### Interactive plot
You can pass a standard ggplot or other plot object to ggplotly() from the plotly package to make your plot interactive.
```{r}
age_outbreak <- incidence(linelist,  date_index = "date_onset", groups = "age_cat", interval = "weekly")
plot(age_outbreak, fill = "age_cat", col_pal = muted, title = "") %>% 
  plotly::ggplotly()
```

### Dynamic table
More info on DT: https://rstudio.github.io/DT/?_ga=2.2810736.1321860763.1619286819-369061888.1601594705
```{r}
DT::datatable(linelist, 
              rownames = FALSE, 
              options = list(pageLength = 5, scrollX = TRUE), 
              class = 'white-space: nowrap' )
```

# Page 1 {data-navmenu="Other page orientations"}
Second level heading are separated into columns (according to initial settings). Second column is divided into tabs.

## Column 1 {data-width=650}
### Dynamic table

## Column 2 {data-width=350 .tabset}
### Epidemic curve by age
### Table

# Page 2 {data-navmenu="Other page orientations" data-orientation=rows}
Second level heading are separated into rows (set in the header of the page).

## Row 1 {data-height=650}
### Trasmission chain (select cases)
## Row 2 {data-height=350}
### Epidemic curve by age
### Table

